---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# statbanktools

<!-- badges: start -->
<!-- badges: end -->

The purpose of statbanktools is to provide a set of helper functions to accompany the statbanker package. statbanktools eases the task of extracting data from CSO tables and generates interactive charts that show the data in levels, differences, and growth rates. The series are stored as an S4 object, which contains the raw data, the transformations of the data, and metadata.

## Installation

You can install the development version of statbanktools from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("xprimexinverse/statbanktools")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(statbanker)
library(plotly)
library(statbanktools)
NAQ01 <- getStatBankData("NAQ01", type = "px")
PCR_SA <- get_series(NAQ01, index = 2)
head(PCR_SA@data,n=20)

```

